sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-04-27 inst/documents/rotations_notes.Rmd
starting paper3 and developing sensi analysis

eek
      0 [main] us 0 init_cheap: VirtualAlloc pointer is null, Win32 error 487
AllocationBase 0x0, BaseAddress 0x68570000, RegionSize 0xE0000, State 0x10000
C:\Program Files (x86)\Git\bin\ssh.exe: *** Couldn't reserve space for cygwin's heap, Win32 error 0
fatal: Could not read from remote repository.

Please make sure you have the correct access rights
and the repository exists.

@@

~ look more at phaps-rotations-better.Rmd

~ seems that min_rwr_interval explains the plots looking different but not the measured gens_under_thresh

@@

# state of play
~ sensi_an_rotations1.Rmd : starting on sensitivity analysis
~~  produces an output dataframe containing both inputs and outputs

@@

>>>>

stackoverflow says this is a cygwin memory error and rebooting should fix it.
eek
0 [main] us 0 init_cheap: VirtualAlloc pointer is null, Win32 error 487
AllocationBase 0x0, BaseAddress 0x68570000, RegionSize 0xE0000, State 0x10000
C:\Program Files (x86)\Git\bin\ssh.exe: *** Couldn't reserve space for cygwin's heap, Win32 error 0
fatal: Could not read from remote repository.

Just rebooted and that fixed it.

*Seems that rotations favoured by higher costs, higher dominance of cost, lower start freq (longer to act), shorter rot interval (more changes)*

*3/4/18*

~ set up initial sensi analysis of 1000 runs
~ 200 runs take < 30 mins

~ seems that a lot of runs don't reach resistance thresholds by 400 generations, and this is with start-freqs set to 0.01, if I set lower start freqs then even more runs will be excluded.

done ~ add ranges for variable params
done ~ copy across grid.arrange from phaps-rotations-better

around 79% of runs failing to make thresholds

upped max gens to 500 and the lower exposure val to try to improve number making thresholds

*4/4/2018*

ooo with new ranges getting a few runs where there is a big advantage to rotation. Seems to be assoc with high dom_cos > 0.8
Only c 1% of scenarios, 2 out of 200

# scenario 137 sum generations deployed insecticide under thresh rotation: 500 sequence: 258
run_rot(n_insecticides=3, cost=0.026, start_freqs=0.032, rot_interval=10, eff=0.5,
dom_sel=0.36, dom_cos=0.82, rr=0.32, expo_hi=0.73, coverage=1,
migration=0, max_gen=500, min_rwr_interval=5)

# scenario 143 sum generations deployed insecticide under thresh rotation: 500 sequence: 126
run_rot(n_insecticides=2, cost=0.049, start_freqs=0.064, rot_interval=0, eff=0.71,
dom_sel=0.089, dom_cos=0.87, rr=0.9, expo_hi=0.65, coverage=1,
migration=0, max_gen=500, min_rwr_interval=5)

In 137 even the rounding makes the rotation last slightly less long (e.g. c400 rather than 500)

start writing code to calc difference between sequence and rotation ready to put that into PRCC.

currently i have repeated following rows for sequence and rotation with identical input params

i probably want to replace this with one row and columns for gens_rot and gens_seq

new version one row per scenario :

#advantage to rotation despite dom_cos=0.23, cost=0.02
#scenario 153 sum generations deployed insecticide under thresh rotation: 406 sequence: 289
run_rot(n_insecticides=4, cost=0.023, start_freqs=0.019, rot_interval=28, eff=0.92,
dom_sel=0.019, dom_cos=0.23, rr=0.63, expo_hi=0.75, coverage=1,
migration=0, max_gen=500, min_rwr_interval=5)

Looking at some more of literature :

From Mallet 1989 :
Since a naive strategy - of using insecticides in turn until resistance evolves to each - gives almost the same total control period as a planned rotation23, rotations can hardly even be defined as management. However, in some cases rotations may be the only practical way of limiting resistance to a single favoured compound 23 27.

23 is curtis 1987 a book chapter I couldn't find.

Curtis 1993 has some good quotes and references about rotations.
It covers the oncheriasis control program which is taken by some to be evidence in favour of rotations
Fig 3 & 4 is lab data comparing sequence & rotation, very similar to our plots, I should definitely cite it.

"A programme such as the OCP differs from these simple models in that more than two insecticides are available for use and a given compound can therefore be out of use for more generations than it is in use."

I hadn't thought of that. Having more than 2 insecticides allows each to be out of use for more time than it is in use. 
So if the increase in resistance while in use was the same as the decrease when not in use then a rotation could be sustainable in the long term. However it is likely that resistance will increase faster in presence than it will decrease in absence (I think Curtis says that too).

Curtis cites how his 1987 work has already included effect of modifier genes, and shows it here in Fig 6.
"Supporters of prearranged rotations usually tacitly or explicitly assume that the general fitness due to resistance genes will improve if they are exposed to selection for many generations. Curtis (1987) simulated the behaviour of a modifer gene which could have this effect and found that it would only have an appreciable influence if one allowed resistance gene frequencies to become very high before switching insecticides.""

"One possible objection to the reactive system is that it requires an efficient and
comprehensive system for testing for resistance to avoid ‘overshooting’ and
getting stuck as in the dotted line in Fig. 6. However, running a prearranged
rotation without a monitoring system would mean that one would have no way
of knowing if the system was still working."

on p16 there is also interesting consideration of what expected in a mixture if one insecticide decays before another.

It's negative about rotations :
'Except where there are seasonal/environmental reasons for a pre-arranged rotation (as in the OCP), we do not find that such rotations are likely to have any advantage over well-managed reactive rotation, and we do not consider that the latter can validly be called a 'strategy' for resistance management. The use of a suitable insecticide mixture seems more promising in the light of the limited data so far available on resistance in relation to insecticide impregnated bednets.'

I would like to get the Curtis 1987 paper
Curtis CF. 1987. Genetic aspects of selection for resistance. In Ford MG, Holloman DW, Khambay BPS,
Sawicki RM, eds. Combating resistance to xenobiotics. Chichester, U.K.: Ellis Horwood, 15e161.

but couldn't find and probably adds little

*5/4/2018*
added progress counter to sensi_an_rotations after 2000 runs failed to finish overnight
also now save the output every 200 runs

100 scenarios take < 10 mins
2000 scenarios should take 20*10 mins, 200 mins < 2 hours
but seems that RAM fills up that may slow it down

got 1400 runs, PC ground to a halt.

No very clear pattern for high difference runs.
Small positice effect with cost & dom_cos, small -ve effect of dom_sel

*9/4/2018*
turned off plotting in sensi_an_rotations
10,000 runs took c 100 minutes (1hr20)

*27/4/2018*

First draft of paper3

trying to get references to work without having to copy the .bib file from resistance

C:/rsprojects/resistance/inst/documents/paper2/

Getting filter pandoc-citeproc' had status 83 Execution halted
https://stackoverflow.com/questions/36826916/pandoc-citeproc-error-83-with-rmarkdown-file

removed all '-' from citation keys in mendeley, didn't fix

Temporary solution of cutting out all refs except 2 from the .bib file fixed it.
Need to go throught the bib file and look for error.
Can I reduce size of the bib file to just the IR papers ? What did I do for ecocrop ?

@@

~ can I add figures from specific sensi_an runs ? or safer to run the model for set runs from the paper rmd.

~ how to sort library.bib ? Have a much reduced copy in rotations folder now.

~ change random seed and run another 1400 runs
~ start PRCC. 
~ can I try a predictive model to predict rot_minus_seq from inputs ?

think about killer plot to display difference between rot & seq generations

be careful that min_rwr_interval doesn't come back to bite me. Ian wanted it different, i.e. not going back to an insecticide that has been used recently ...

~ *decide on min_rwr_interval for sensi analysis
~ decide on max_gen, what was it for paper1 ?
~ one generation per month, 12 generations per year, 500 gens is ~40 years

@@

# good refs for paper
resistance : malERA2017_updated-research-agenda-resistance-in-malaria.pdf

"What are the benefits of insecticide rotations, mixtures, or spatial mosaics of different compounds?
What is the impact of adding nonpyrethroid IRS where LLINs are already deployed at high coverage and quality? When should new insecticides be adopted? What is the ideal rotation period or mosaic configuration? How many insecticide classes are needed for effective rotation or mosaic strategies? Despite the absence of data to answer these questions, some countries have already developed operational frameworks for resistance management that could be adopted by other programmes.""

The malERA Refresh Consultative Panel on Insecticide and Drug Resistance (2017) malERA: An updated research agenda for insecticide and drug resistance in malaria elimination and eradication. PLoS Med 14(11): e1002450. https://doi.org/10.1371/journal.pmed.1002450

# state of play
~ sensi_an_rotations1.Rmd : starting on sensitivity analysis
~~  produces an output dataframe containing both inputs and outputs
~~ saves outputs to df_res_all_rot.rda

@@

# useful
~ one generation per month, 12 generations per year, 500 gens is ~40 years

### 2018-04-27 inst/documents/sensi_an_rotations1.Rmd
starting paper3 and developing sensi analysis

Starting question : is there any benefit to rotations when there are no costs and no migration to an untreated area ?

Test 1. No refugia (i.e. Coverage=100%) or fitness costs. Would expect all policies to be equivalent.

Test 2. Dominance of resistance and fitness costs both set to 0.5.
I suspect one of the advantages of rotations (and the presence of refugia) is that they maintain lower resistance allele frequencies which slows the spread of recessive resistance alleles. I suspect/guess/intuit that if we make them semi-dominate these effects should disappear and all policies should be the same. I’m probably wrong but it’s a nice test…..

Testing sensitvity analysis to answer question 1. Are sequences and rotations equivalent when coverage 100% and no fitness costs. On each page should see a run with 1 set of inputs first for sequence then for rotation.

@@

n_scenarios <- 200

df_res_all <- data.frame()

for(i in 1:n_scenarios)
{
  # inputs (could also be saved to a dataframe first & extracted one row at a time)
  linputs <- list()

@@

  ## constant inputs ##
  linputs$coverage <- 1
  linputs$migration <- 0
  #linputs$cost <- 0 #variable cost below
  linputs$max_gen <- 500

@@

  #random rot interval integer
  linputs$rot_interval <-   sample( 5:50, 1 )  #beware set replace=T if more than 1

@@

  # to compare sequence to rotation run all the scenarios above for both seq & rot 
  # beware has to be 1:0 because interval is overwritten for seq
  for(rot_or_not in 1:0)
  {  
    #to get rot_int of 0 every other run
    if (rot_or_not == 0) linputs$rot_interval <- 0

@@

    # summarise results per scenario
    # NOTE this is also currently calc at end of run_rot() here or other post-process is probably better
    # and put in the output dfres, but the value has to be rpeated for every generation 
    res <- dfres %>%
      # only assess in control areas not in refugia  
      dplyr::filter(active_or_refuge=='active') %>%
      group_by(resist_gene) %>%
      # for all insecticides in all generations  
      # summarise(gens_under50 = sum(resistance < 0.5, na.rm=TRUE)) %>%
      # summarise(mean_gens_under50 = mean(gens_under50)) %>%
      # just for deployed insecticides 
      summarise(gens_dep_under50 = sum(resistance < 0.5 &
                                       #finds insecticide in use = this one
                                       resist_gene==paste0('insecticide',insecticide), na.rm=TRUE)) %>%
      summarise(tot_gens_dep_under50 = sum(gens_dep_under50)) %>%    
      unlist()

    # create dataframe from inputs and outputs
    # first add scenario column onto results
    res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, res))

@@

    ggres <- rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=FALSE)
    gens_res <- as.numeric(gens_under_thresh(dfres))

    # to plot results for checking
    if ( linputs$rot_interval == 0 )
    {
      ggseq <- ggres
      gens_seq <- gens_res
    } else
    {
      ggrot <- ggres
      gens_rot <- gens_res
    }

  #printing input values
  #print(unlist(linputs))

  # try to plot input vals instead
  # extract out those between 0 & 1
  dfi <- data.frame(t(as.data.frame(linputs)))
  names(dfi) <- 'value'
  dfi$inputs <- rownames(dfi)

@@

@@

# save object containing inputs and results as rda for analysis
save(df_res_all, file='df_res_all_rot.rda') #paste0(outFolder,'*.rda'))

@@

# summary plot of all runs, would show any differences between sequence & rotations as non horizontal lines

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=6}

@@

@@

# check proportion of scenarios not reaching thresholds by max_runs

    nruns_fail <- df_res_all %>% 
                  filter(tot_gens_dep_under50 == linputs$max_gen) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs not reaching thresholds : ', nruns_fail/(2*n_scenarios) ) #2* beacuse eeach scenario run for seq & rot

>>>>

10,000 runs comparing rotations and sequences.

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
#eval=FALSE just to temporarily hide this text

# Starting question : is there any benefit to rotations when there are no costs and no migration to an untreated area ?
# 
# Test 1. No refugia (i.e. Coverage=100%) or fitness costs. Would expect all policies to be equivalent.
# 
# Test 2. Dominance of resistance and fitness costs both set to 0.5.
# I suspect one of the advantages of rotations (and the presence of refugia) is that they maintain lower resistance allele frequencies which slows the spread of recessive resistance alleles. I suspect/guess/intuit that if we make them semi-dominate these effects should disappear and all policies should be the same. I’m probably wrong but it’s a nice test…..
# 
# 
# Testing sensitvity analysis to answer question 1. Are sequences and rotations equivalent when coverage 100% and no fitness costs. On each page should see a run with 1 set of inputs first for sequence then for rotation.

#\pagebreak
```

@@

# set random seed so that results can be reproduced
#set.seed(1)
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10000
already_ran     <- TRUE

# if already done runs, just load data for plots
if (already_ran)
{
  #C:/rsprojects/rotations/inst/documents/

  load("df_res_all_rot10000.rda")

}else
{
  df_res_all <- data.frame()

  for(i in 1:n_scenarios)
  {
    #message should output to the R markdown console
    if (i%%500 == 1) message("scenario ",i," of ",n_scenarios," ",Sys.time())

    # inputs (could also be saved to a dataframe first & extracted one row at a time)
    linputs <- list()

@@

    ## constant inputs ##
    linputs$coverage <- 1
    linputs$migration <- 0
    #linputs$cost <- 0 #variable cost below
    linputs$max_gen <- max_gen

@@

@@

    # to compare sequence to rotation run all the scenarios above for both seq & rot 
    for(rot_or_not in 0:1)
    {  
      #to get rot_int of 0 every other run
      if (rot_or_not == 0) linputs$rot_interval <- 0
      else   #random rot interval integer
          linputs$rot_interval <-   sample( 5:50, 1 )  #beware set replace=T if more than 1

@@

      # summarise results per scenario
      # note this is also currently calc at end of run_rot() here is probably better

      res <- gens_under_thresh(dfres)

      # to plot results for checking
      if ( linputs$rot_interval == 0 )
      {
        gens_seq <- as.numeric(res)
      } else
      {
        gens_rot <- as.numeric(res)
      }

      if (plot_scenarios)
      {
        # make plot
        ggres <- rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=FALSE)

        # to plot results for checking
        if ( linputs$rot_interval == 0 )
        {
          ggseq <- ggres
          gens_seq <- as.numeric(res)
        } else
        {
          ggrot <- ggres
          gens_rot <- as.numeric(res)
        }
      }

    # TODO I may want to concat all dfres into one object (adda column for scenario num) to save for later analysis
    # e.g. if I wanted to calculate average resistance frequencies over time in addition to gens below threshold

    # make an output row for each scenario with inputs, gens_rot, gens_seq
    # need to make sure I retain the rot_interval for rot

    # add scenario id column onto results
    res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

@@

    if (plot_scenarios)
    {  
      # plot input vals
      # extract out those between 0 & 1
      dfi <- data.frame(t(as.data.frame(linputs)))
      names(dfi) <- 'value'
      dfi$inputs <- rownames(dfi)

@@

    }

    #I could save partial outputs every 200 scenarios
    #just in case doesn't make to end
    if (i%%1000 == 0)
    {
      #df_res_all$rot_minus_seq <- df_res_all$gens_rot - df_res_all$gens_seq

      # save object containing inputs and results as rda for analysis
      save(df_res_all, file='df_res_all_rot.rda') #paste0(outFolder,'*.rda'))    
    }

@@

}

# proportion of scenarios not reaching resistance thresholds

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
# check proportion of scenarios not reaching thresholds by max_runs for both seq & rot

    nruns_fail <- df_res_all %>% 
                  filter(gens_seq == max_gen & gens_rot == max_gen) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs not reaching thresholds : ', nruns_fail/nrow(df_res_all) )

    # remove runs where thresholds not reached for seq & rot 
    df_res_all <- df_res_all %>% 
                  filter(gens_seq != max_gen | gens_rot != max_gen)

    nruns_same <- df_res_all %>% 
                  filter(gens_seq == gens_rot) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs (that did reach threshold) where rotations and sequence the same  : ', nruns_same/nrow(df_res_all) )

    nruns_rot_20pc_better <- df_res_all %>% 
                  filter(rot_minus_seq/gens_seq >= 0.2 ) %>%
                  summarise(n=n()) %>% 
                  unlist()

    cat('proportion runs (that did reach threshold) where rotations >20 % better than sequence  : ', nruns_rot_20pc_better/nrow(df_res_all) )

# difference between rotations and sequences across all runs

## mostly (~67%) no difference but infrequent where rotations better
## ~ 7% of runs, rotation at least 20% better than sequence

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

    print( ggplot(df_res_all, aes(x=rot_minus_seq)) +

             geom_histogram(binwidth=10) +
             xlab('rot_minus_seq : rotation generations minus sequence') +
             ylab('count (sqrt scale to show low values)') +
             scale_y_sqrt(breaks=c(0,10,20,50,200,500,2000,5000)) + #can't use log scale because anchored at 0
             theme_minimal() +
             theme(panel.grid.minor.y=element_blank()))

@@

# Examples of runs where rotations > 20% better than sequences

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=3.5}

scenarios_to_plot <- c(624,2167,602,4028,5771)

for(scenario in scenarios_to_plot)
{
  cat(scenario,"\n")

  linputs <- as.list( df_res_all[scenario, 1:15] )

  # run one scenario
  dfres <- do.call(run_rot, linputs)

  rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=TRUE)

  #now run as sequence
  linputs$rot_interval <- 0
  dfres <- do.call(run_rot, linputs)

  rot_plot_resistance(dfres, plot_refuge=FALSE, logy=FALSE, plot=TRUE)

  dfi <- data.frame(t(as.data.frame(linputs)))
  names(dfi) <- 'value'
  dfi$inputs <- rownames(dfi)

  ggins <- ggplot(dfi, aes(x=inputs,y=value)) + 
            geom_point() +
            theme_minimal() +
            ylim(0,1) +
            theme(axis.text.x = element_text(angle = 20,hjust = 1, vjust = 1))
  plot(ggins)

}

#How does the difference between rotations and sequences respond to model inputs ?
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

# go through selected inputs and plot them on x with rot_minus_seq on y 
# initially with 200 reps doesn't show anything obvious, try it with 2000 overnight runs
in_cols <- c('cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs')

y <- 'rot_minus_seq'

for(i in in_cols)
{

    #plotnum <- plotnum + 1

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    #plotlist[[plotnum]] <- 
    print( ggplot(df_res_all, aes_string(x=i, y=y)) +

             geom_point(shape=1, size=1, alpha=0.5, show.legend=FALSE) +
             theme_minimal() +
             geom_smooth(linetype='dashed',size=0.5) )

}

# PRCC

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

  library(sensitivity)

# pcc(X, y, rank = FALSE, nboot = 0, conf = 0.95)
# 
# Arguments
# X a data frame containing model input variables
# y a vector containing the responses 
# rank logical. If TRUE, the analysis is done on the ranks.
# nboot the number of bootstrap replicates.
# conf the confidence level of the bootstrap confidence intervals.

#same as above
in_cols <- c('cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs')

    x <- df_res_all[,in_cols]
    y <- df_res_all['rot_minus_seq']

    pcc_res <- pcc(x, y, rank=TRUE)

    #if you add bootstrap, error bars are added to the default plot & extra columns to the PRCC object
    #pcc_res <- pcc(x, y, rank=TRUE, nboot=100)
    #plot(pcc_res)

    #results are here I can probably rbind them together into a df that I can ggplot
    #pcc_res$PRCC

    to_plot <- pcc_res$PRCC
    #rename column 1 from 'original to PRCC
    names(to_plot)[1] <- 'PRCC'
    to_plot$inputs <- rownames(to_plot)

    axis_text_x <- element_text(angle = 45,hjust = 1, vjust = 1)
    height <- 0.9

    gg <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             #ggtitle(paste(strat_name[strategy_num])) +
             xlab(NULL)

  #to put back in some ref gridlines that are removed by cowplot
  #theme_set(theme_gray())
  #theme_set(theme_bw())

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.6), labels='AUTO')

# Runs where rotations are >20% better (in red) are associated with higher dominance of cost and lower dominance of selection

# but that does not guarantee, must be interaction with other inputs too.

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

#'cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs'

#'cost','dom_cos','dom_sel'

y <- 'rot_minus_seq'

ggplot(df_res_all, aes(x=dom_sel, y=dom_cos)) + 
     geom_point(shape=3, size=1, alpha=0.2, show.legend=FALSE) +
     theme_minimal() +
     geom_point(data=filter(df_res_all, rot_minus_seq/gens_seq >= 0.3 ), shape=1, size=1, col='red', alpha=0.8)

# looking at modelling it
# library(mgcv)
# mod_lm2 <- gam(rot_minus_seq ~ cost + dom_cos + dom_sel, data=df_res_all)
# summary(mod_lm2)  
# 
# mod_gam2 <- gam(rot_minus_seq ~ s(cost) + s(dom_cos) + s(dom_sel) + s(rr) + s(expo_hi) + s(male_expo_prop) + s(eff) + s(start_freqs), data=df_res_all)
# 
# summary(mod_gam2)  
# #Deviance explained = 19.5%
# 
# mod_gam3 <- gam(rot_minus_seq ~ te(cost,dom_cos,dom_sel), data=df_res_all)
# summary(mod_gam3)

#actually decision trees may be useful

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=6}
#eval=FALSE tmp because changes above will break this
# summary plot of all runs, would show any differences between sequence & rotations as non horizontal lines

@@

#it was useful for me but now that I've moved to one row per scenario it won't work !!

@@
